Reproducible psychological research and project management in R

### 2019-10-09 docs/slides/vertical_intro.Rmd
update slides

class: pink, center, middle, clear

# Everything in its right place - Radiohead

@@

# Hodge Podge Management

@@

# Solution Stack Management

From Wikipedia: In computing, a **solution stack or software stack** is a set of software subsystems or components needed to create a complete platform such that no additional software is needed to support applications. Applications are said to "run on" or "run on top of" the resulting platform.

# R as a solution stack

@@

# R as a control center

Having a full solution stack in R doesn't mean you can't use other things.

R can often be used as a control center to run other code (e.g., python, C++, etc.)

@@

>>>>

# link to this website

Contains these slides and example of using R to share many components of a research project

<https://crumplab.github.io/vertical/>

@@

# Online Resources for R

Lots of great and free online resources. I've been making a list:

<https://crumplab.github.io/blogposts/LearningR/LearningR.html>

# Everything everywhere workflow

@@

# vertical: R for everything

@@

# R markdown (.Rmd files)

A text file for **notes and R scripts** that compiles to different formats (html, pdf, etc.)

```{r}
knitr::include_graphics("imgs/rmarkdown.png")
```

@@

# R Markdown guide

Definitive guide to R Markdown

<https://bookdown.org/yihui/rmarkdown/>

# Experiments in R (jsPsych)

- jsPsych documentation <https://www.jspsych.org>
- xprmntr R package (in dev) <https://github.com/CrumpLab/xprmntr>
- examples <https://github.com/CrumpLab/jsPsychRexamples>

# Data analysis

- tidyverse <https://www.tidyverse.org> lots of great packages for data analysis
- dplyr <https://dplyr.tidyverse.org> data-wrangling
- ggplot2 <https://ggplot2.tidyverse.org> plotting

# Data frames

```{r, echo=TRUE}
all_data <- data.frame(trial = 1:6,
                       congruency = rep(c("con","inc"), each = 3),
                       rt = rnorm(6, mean = 0, sd = 100),
                       accuracy = c(1,1,1,1,0,1))
all_data
```

# dplyr - tidyverse Data Wrangling

```{r, echo=T}
library(tidyverse)
df <- all_data %>%
  filter(accuracy == 1) %>%
  group_by(congruency) %>%
  summarise(mean_rt = mean(rt))
df
```

# ggplot2 - tidyverse plotting

```{r, echo=TRUE, fig.height=3}
ggplot(df, aes(x=congruency, y=mean_rt))+
  geom_bar(stat="identity", position="dodge") +
  theme_classic()
```

# slide decks

This slide deck was written in R markdown the`xaringan` package

<https://github.com/yihui/xaringan>

# APA papers

`papaja` is an R package for writing APA papers in R markdown (then compile to .pdf)

<https://crsh.github.io/papaja_man/>

# R packages and pkgdown

`pkgdown` is an R package that builds a website for R packages.

<https://pkgdown.r-lib.org>

# bookdown

A package for writing books (compile to web-book, .pdf, and epub)

<https://bookdown.org>

# R markdown websites

Write in R markdown, and make all kinds of websites

<https://rmarkdown.rstudio.com/lesson-13.html>
